Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
added some text to wrap App. A

\section{Method details}
\label{app:method}
%
As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters. We show here how we can derive them in general for the family of exponential likelihoods. By rewriting the loss in the natural form, we have,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
\end{equation}
\todo{check the signs with the main paper}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

@@

\subsection{Computational complexity}

>>>>

\section{Method details}
\label{app:method}
In this section, we first show in \cref{app:losses} how the dual parameters used for \our are computed for the different losses employed in our experiments, and then we discuss the computational complexity of our method in \cref{app:comp_compl}.
%
\subsection{Computation of the dual parameters for different losses}\todo{just a placeholder}
\label{app:losses}
As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters. We show here how we can derive them in general for the family of exponential likelihoods. By rewriting the loss in the natural form, we have,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
\end{equation}
\todo{check the signs with the main paper}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

@@

\subsection{Computational complexity}
\label{app:comp_compl}
